---
title: "Job Market Hub"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(lubridate)
library(googlesheets4)
library(kableExtra)
library(fontawesome)

## package global options
# skip googlesheets login
gs4_deauth()

## Set date threshold to display jobs
t = "2023-09-10"
```

## Welcome!

This page is for internal use only. If you are not a letter writer, I encourage you to use the navigation tab on top to learn more about me and my work.

## Upcoming Deadlines

```{r, message = FALSE}
jobs = read_sheet("https://docs.google.com/spreadsheets/d/1wCTQQpg9AALD-d4N2gCD-_xrV_P-EhNJUeDQnUsVHPI/edit#gid=505775282",
                  sheet = 1)

# some manipulation to show only what is useful
jobs = jobs %>% 
# don't show if already applied
  filter(is.na(applied)) %>% 
# filter deadlines within treshold
filter(as_date(deadline) <= as_date(t)) %>% 
  mutate(
  # url = paste0('<a href="', url,'"target="_blank"></a>'),
  deadline = format(deadline, "%B %e, %Y")
)
```

**Last update:** `r format(Sys.Date(), "%B %e, %Y")`. Full list [here](https://docs.google.com/spreadsheets/d/1wCTQQpg9AALD-d4N2gCD-_xrV_P-EhNJUeDQnUsVHPI/edit#gid=1630537882).

**Number of letters to write:**

```{r}
jobs %>% 
  summarize(across(Gisela:Michelle, ~ sum(.x, na.rm = TRUE))) %>% 
  select_if(~sum(.) > 0) %>% 
  kbl() %>% 
  kable_paper(full_width = FALSE, position = "left")
```

&nbsp;

```{r, results = "asis"}
refs = jobs %>% select(Gisela:Michelle)

# try a loop now
for(i in 1:nrow(jobs)){
  cat("[**",
      jobs$position[i], " - ",
      jobs$department[i], " - ",
      jobs$place[i],
      paste0('**](', jobs$url[i],')'),
      "<br/>",
      sep = "")
  
  cat("**Letters:**",
      paste(colnames(refs)[which(refs[i,] == 1)], collapse = ", "),
      "<br/>",
      "**Deadline:**", jobs$deadline[i],
      "<br/>",
      "**Delivery:**", jobs$letters[i],
      "<br/>",
      "**Notes:**", jobs$notes[i],
      "<br/>")
  
  cat(rep("&nbsp;  ", 2), sep="\n")
}
```


## Materials

- Cover letter [`[Methods]`](job_market/cover_letter/cover_letter_methods.pdf) [`[Comparative]`](job_market/cover_letter/cover_letter_cp.pdf)

- Research statement [`[Methods]`](job_market/statements/research_statement_methods.pdf) [`[Comparative]`](job_market/statements/research_statement_cp.pdf) 

- Teaching statement
[`[Methods]`](job_market/statements/teaching_statement_methods.pdf) [`[Comparative]`](job_market/statements/teaching_statement_cp.pdf) 

- Diversity statement [Coming soon!]

## Research

Highlights here. See the [research](/research.html) tab for more.

### Methods

1. **Assessing the Validity of Prevalence Estimates in Double List Experiments**  
*Journal of Experimental Political Science*  
[`Paper`](files/research/dle_test.pdf)   [`Appendix`](files/research/dle_test_appendix.pdf)

    - Review process complete, official version should come soon
    - I started working on this *before* working on my dissertation!
  
2. **Balancing Precision and Retention in Experimental Design**  
with [Erin Rossiter](http://erossiter.com/)  
[`Paper`](https://gustavodiaz.org/files/research/precision_retention.pdf) [`Appendix`](https://gustavodiaz.org/files/research/precision_retention_appendix.pdf)

    - Under review in APSR
    
3. **List experiment and Network Scale-up questions to measure criminal governance strategies in Uruguay**  
with [Ines Fynn](https://imfd.cl/en/investigador/ines-fynn/), [Verónica Pérez Bentancur](https://scholar.google.com/citations?user=wj21dxsAAAAJ&hl=en), and [Lucía Tiscornia](https://www.luciatiscornia.com/)

    - Ongoing project that should yield 4 papers:
    1. Combining list experiments and network scale-up questions to improve measurement of sensitive attitudes (Presenting at Polmeth, Maplemeth, Toronto Behavior Workshop, maybe LAPolmeth)
    2. Recovering estimates when placebo statements mess up your list experiment
    3. Short piece documenting extent of criminal governance activity in a context of low crime and high state presence (Presenting at APSA)
    4. Longer piece same as (3) but delving deeper into theory and field interviews
  
4. **Survey Experiments and the Quest for Valid Interpretation**  
with [Christopher Grady](https://publish.illinois.edu/cdgrady2/) and [James H. Kuklinski](https://pol.illinois.edu/directory/profile/kuklinsk)  
In: *Luigi Curini and Robert Franzese (eds)*  
*The SAGE Handbook of Research Methods in Political Science and International Relations*, 2020  
[`Chapter`](files/research/sage_survey_experiments_chapter.pdf) [`Handbook`](https://us.sagepub.com/en-us/nam/the-sage-handbook-of-research-methods-in-political-science-and-international-relations/book262875)

### Comparative


1. **Ignoring Female Performance: A Survey Experiment on Policy Implementation in Argentina**  
with [Virginia Oliveros](https://virginiaoliveros.com/), [Rebecca Weitz-Shapiro](https://vivo.brown.edu/display/rweitzsh), and [Matthew S. Winters](https://sites.google.com/site/mswinters1/)  
[`Paper`](https://gustavodiaz.org/files/research/gender_performance.pdf) [`Appendix`](https://gustavodiaz.org/files/research/gender_performance_appendix.pdf)

    - Under review at BJPS
    
2. **Mayors Alter Spending to Counter the Electoral Consequences of Increased Monitoring: Evidence from Anti-Corruption Audits in Brazil**  
[`Paper`](files/research/audit_spending.pdf)

    - Presenting at APSA. Presented in political economy of development workshop organized by the *Journal of Public Policy*

3. **Revealing Nearby Corruption Drives Party Switching: Evidence from Local Level Audits in Brazil**   
[`Paper`](files/research/nearby_corruption.pdf)

    - Old job talk

    
4. **Light in the Midst of Chaos: COVID-19 and Female Political Representation**  
with [Kelly Senters Piazza](https://www.usafa.edu/facultyprofile/?smid=23816)  
*World Development* 136: 105125, 2020  
[`Paper`](https://doi.org/10.1016/j.worlddev.2020.105125)



## Teaching

- McMaster course website: [popw23.gustavodiaz.org](https://popw23.gustavodiaz.org/)

- [Syllabi](/teaching.html)

- [Teaching evaluations](/job_market/statements/diaz_teaching_evals.pdf)

    - I have not included it in yet but my recent course at Mac only got like 3 reviews...

## Other stuff

Section in progress. Things that may be missing or understated in current materials.

- Building a text analysis pipeline to analyze citation patterns in methodology across social sciences as part of postdoc duties

- Dissertation data is original combines text analysis and supervised learning to create most up to date data set of Brazilian local anti-corruption audits

- Dissertation got poster award at Latin American Polmeth 2019

- Cool places I have interviewed but not taken jobs at that may make people feel like they need to hire me before someone else does: 

> Penn State, University of Konstanz, University of Birmingham, Howard University, William & Mary, KDI School of Public Policy and Management, Carlos III-Juan March Institute of Social Sciences, University of Melbourne

- Went to EITM at Emory in 2019

- Have experience mentoring an undergrad RA. Used it as an excuse so we could both learn text analysis. Student got job as data consultant after college. I claim all the credit

- Last 3 years have been marked by: Pandemic, parenting, moving, escaping from hurricane, immigration troubles, family illness. This is the first summer since 2020 without a major life thing going on. Feel free to weave that in your assessment of my productivity if you feel it may help
