---
title: "Job Market Hub"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(lubridate)
library(googlesheets4)
library(kableExtra)
library(fontawesome)

## package global options
# skip googlesheets login
gs4_deauth()

## Set date threshold to display jobs
t = "2022-09-05"
```

## Welcome!

This page is for internal use only. If you are not a letter writer, I encourage you to use the navigation tab on top to learn more about me and my work.

## Upcoming Deadlines

```{r, message = FALSE}
jobs = read_sheet("https://docs.google.com/spreadsheets/d/1wCTQQpg9AALD-d4N2gCD-_xrV_P-EhNJUeDQnUsVHPI/edit#gid=505775282")

# some manipulation to show only what is useful
jobs = jobs %>% 
# don't show if already applied
  filter(is.na(applied)) %>% 
# filter deadlines within treshold
filter(as_date(deadline) <= as_date(t)) %>% 
  mutate(
  # url = paste0('<a href="', url,'"target="_blank"></a>'),
  deadline = format(deadline, "%B %d, %Y")
)
```

**Last update:** `r format(Sys.Date(), "%B %d, %Y")`. Full list [here](https://docs.google.com/spreadsheets/d/1wCTQQpg9AALD-d4N2gCD-_xrV_P-EhNJUeDQnUsVHPI/edit#gid=505775282).

**Number of letters to write:**

```{r}
jobs %>% 
  summarize(across(Avital:Michelle, ~ sum(.x, na.rm = TRUE))) %>% 
  select_if(~sum(.) > 0) %>% 
  kbl() %>% 
  kable_paper(full_width = FALSE, position = "left")
```

&nbsp;

```{r, results = "asis"}
refs = jobs %>% select(Avital:Michelle)

# try a loop now
for(i in 1:nrow(jobs)){
  cat("[**",
      jobs$position[i], " - ",
      jobs$department[i], " - ",
      jobs$place[i],
      paste0('**](', jobs$url[i],')'),
      "<br/>",
      sep = "")
  
  cat("**Letters:**",
      paste(colnames(refs)[which(refs[i,] == 1)], collapse = ", "),
      "<br/>",
      "**Deadline:**", jobs$deadline[i],
      "<br/>",
      "**Delivery:**", jobs$letters[i],
      "<br/>",
      "**Notes:**", jobs$notes[i],
      "<br/>")
  
  cat(rep("&nbsp;  ", 2), sep="\n")
}
```


## Materials

- Cover letter [`[Comparative]`](job_market/cover_letter/cover_letter_cp.pdf) [`[Methods]`](job_market/cover_letter/cover_letter_methods.pdf)

- Research statement [`[Comparative]`](job_market/statements/research_statement_cp.pdf) [`[Methods]`](job_market/statements/research_statement_methods.pdf)

- Teaching statement [`[Comparative]`](job_market/statements/teaching_statement_cp.pdf) [`[Methods]`](job_market/statements/teaching_statement_methods.pdf)

## Writing Samples

Mix and match depending on application. See the [research](/research.html) tab for more.

### Comparative

1. ["Revealing Nearby Corruption Drives Party Switching: Evidence from Local Level Audits in Brazil"](files/research/nearby_corruption.pdf)

    - CP Job talk
    - New version going for review soon!
  
2. ["Mayors Alter Spending to Counter the Electoral Consequences of Increased Monitoring: Evidence from Anti-Corruption Audits in Brazil"](files/research/audit_spending.pdf)

    - Invited to present in political economy of development workshop organized by the *Journal of Public Policy*
  
3. ["Light in the Midst of Chaos: COVID-19 and Female Political Representation."](https://doi.org/10.1016/j.worlddev.2020.105125) *World Development* 136: 105125 (with [Kelly Senters Piazza](https://www.usafa.edu/facultyprofile/?smid=23816))

4. *Include paper with Virginia, Rebecca, and Matt here when available*


### Methods

1. ["Assessing the Validity of Prevalence Estimates in Double List Experiments."](files/research/dle_test.pdf)

    - **R&R** in *Journal of Experimental Political Science*
    - Methods job talk
  
2. ["Balancing Precision and Retention in Experimental Design"](files/research/precision_retention.pdf) (with [Erin Rossiter](http://erossiter.com/))

    - Public version coming in August
  
3. ["A Model Selection Approach to Geographic Spillovers."](files/research/model_spillovers.pdf)

    - Best poster award. 2019 Latin American Political Methodology Meeting
    - Rewriting as a research note!



## Teaching

- [Syllabi](/teaching.html)

- [Teaching evaluations](/job_market/statements/diaz_teaching_evals.pdf)
