---
format:
  revealjs:
    embed-resources: true
    slide-number: true
---

::: {style="text-align: center"}
## Combining List Experiments and the Network Scale Up Method {.center .smaller}

::: columns

::: {.column width="50%"}
**Gustavo Díaz**  
McMaster University  
<diazg2@mcmaster.ca>  
[{{< fa brands twitter >}} @gusvalo](https://twitter.com/Gusvalo)

**Verónica Pérez Bentancur**  
Universidad de la República
<veronica.perez@cienciassociales.edu.uy>  
[{{< fa brands twitter >}} @veroperezben](https://twitter.com/veroperezben)
:::

::: {.column width="50%"}
**Ines Fynn**  
Pontificia Universidad Católica de Chile  
<ifynn@uc.cl>  
[{{< fa brands twitter >}} @ifynn_](https://twitter.com/ifynn_)

**Lucía Tiscornia**  
University College Dublin  
<lucia.tiscornia@ucd.ie>  
[{{< fa brands twitter >}} @tiscornia21](https://twitter.com/tiscornia21)

:::

:::

&nbsp;

Slides: [gustavodiaz.org/maplemeth](https://gustavodiaz.org/maplemeth.html)

:::



```{r include=FALSE}
library(knitr)

opts_chunk$set(fig.pos = "center", echo = FALSE, 
               message = FALSE, warning = FALSE)
```

```{r setup}
# Packages
library(tidyverse)
library(DeclareDesign)
library(kableExtra)


# ggplot global options
theme_set(theme_gray(base_size = 20))
```

## First slide

Hello!

::: aside
This goes on the bottom!
:::
